 \chapter{Discussion and conclusion}
 \label{chapter:discussion}
 

 %Task1: Compare  expectations and our results
 In the first task the different parts of the far field function could be viewed in the plots, I have not found any reference for this function yet, but it appear to correspond to the analytical expression. Thus the conclusion is that the MATLAB function works correctly. 
 
 
 %Task 2: Compare  expectations and our results
 In task 2 the result of the total radiation the result gave the same for every polarization, as expected. 
 
 
In task 3 the patterns of the far field function were plotted when normalized with respect to the total radiated power in the E- and H-plane. These patterns do resemble the expected result.
 
 
 
 In the fourth task the different parts of the far field function could be viewed in the plots for a given current I, as a arbitrary current was chosen it was somewhat difficult to analyze the result. The result resembles the result in task 1 somewhat. Thus the conclusion is that the MATLAB function works correctly.
 
%Task5:  Compare  expectations and our results
In task 5 it can be noted that the MATLAB function gives the expected phase difference for the equispaced 
 array as the phase linearly increases with the distance from the origin. Simultaneously the phase difference between the individual neighbor elements remained constant through out the array. 
 
 In task 6 the patterns are quite symmetric, which was expected. Giving the conclusion that the MATLAB function is correct. 